EEG Waveform Analysis of P300 ERP with applications to Brain Computer Interfaces

### 2018-09-24 sensors.tex
The abstract was modified

% Abstract (Do not use inserted blank lines, i.e. \\) 
\abstract{The Electroencephalography (EEG) is not just a mere clinical tool anymore.  It has become the de-facto mobile, portable, non-invasive brain imaging sensor to harness brain information in real time and translating or decoding brain signals that can be used to diagnose disease or implement Human Computer Interaction devices.  The automatic processing approach which is based on using quantitative algorithms to detect the cloaked information buried in the signal, outshines the research done by the clinical EEG community which was based intensively on EEG waveforms and the structure of signal plots.  Hence, the purpose of this work is to establish a bridge to fill this gap by reviewing and describing the procedures that have been used to detect patterns in the electroencephalographic waveforms, benchmarking them on a controlled pseudo-real dataset of an ERP waveform and verifying their performance on a public dataset of a BCI Competition.}

>>>>

% Abstract (Do not use inserted blank lines, i.e. \\) 
\abstract{The Electroencephalography (EEG) is not just a mere clinical tool anymore.  It has become the de-facto mobile, portable, non-invasive brain imaging sensor to harness brain information in real time.  It is now being used to translate or decode brain signals to diagnose disease or implement Human Computer Interaction devices.  The automatic processing approach which is based on using quantitative algorithms to detect the cloaked information buried in the signal, outshines the research done by the clinical EEG community.  Clinical EEG is based intensively on waveforms and the structure of signal plots.  Hence, the purpose of this work is to establish a bridge to fill this gap by reviewing and describing the procedures that have been used to detect patterns in the electroencephalographic waveforms, benchmarking them on a controlled pseudo-real dataset of an EEG Event Related Potentials waveform and verifying their performance on a public dataset of a BCI Competition.}
